---
title: "monthly_forecasting"
author: "SOBOYEJO LUKMAN ADEBOYE"
date: "01/06/2020"
output: word_document
always_allow_html: true
---

```{r global_options, include = FALSE}
knitr::opts_knit$set(echo= FALSE)
```

## Packages Installed -------------------------------------------------------------------------#
```{r, warning= FALSE}
# pkgs <-
  (c("forecast", "patchwork", "ggplot2", "plotly", "tidyverse", "pander", "ggthemes", "reshape", "cowplot", "imputeTS", "dplyr"))
# install.packages(pkgs)

library(forecast)   # For the moving avearage timeseries
library(patchwork)  # For combining plots
library(ggplot2)    # For Visualization
library(plotly)     # For interactive plot
library(lubridate)  #
library(knitr)
library(tidyverse)
library(pander)
library(ggthemes)
library(reshape2)
library(cowplot)
library(imputeTS)
library(dplyr)
```


## Read file into R ---
```{r}

# Monthly Time series
rm(list=ls(all=TRUE))
library(RCurl)
san.mon.data = read.table(text=getURL("https://raw.githubusercontent.com/lukeng200/MSc_Coastal_Drainage_Analysis/master/data_csv/san.mon.csv"),
                  header = T,sep = ",")
# Date Conversion to POSXCIT
san.parse.date <- mutate(san.mon.data, parse.date = parse_date_time(year, "by"))
san.newdate <- mutate(san.parse.date, newdate = as.Date(parse.date))
san.mon <- mutate(san.newdate, year = as.POSIXlt(newdate)$year + 1900)
str(san.mon)
head(san.mon)


# Rasponi Basin Data
ras.mon.data = read.table(text=getURL("https://raw.githubusercontent.com/lukeng200/MSc_Coastal_Drainage_Analysis/master/data_csv/ras.mon.csv"),
                  header = T,sep = ",")
# Date Conversion to POSXCIT
ras.parse.date <- mutate(ras.mon.data, parse.date = parse_date_time(year, "by"))
ras.newdate <- mutate(ras.parse.date, newdate = as.Date(parse.date))
ras.mon <- mutate(ras.newdate, year = as.POSIXlt(newdate)$year + 1900)
str(ras.mon)
head(ras.mon)



# Quinto Basin Data
quin.mon.data = read.table(text=getURL("https://raw.githubusercontent.com/lukeng200/MSc_Coastal_Drainage_Analysis/master/data_csv/quin.mon.csv"),
                  header = T,sep = ",")
# Date Conversion to POSXCIT
quin.parse.date <- mutate(quin.mon.data, parse.date = parse_date_time(year, "by"))
quin.newdate <- mutate(quin.parse.date, newdate = as.Date(parse.date))
quin.mon <- mutate(quin.newdate, year = as.POSIXlt(newdate)$year + 1900)
str(quin.mon)
head(quin.mon)

# # kable()
# # pander()
```


# Precipitation ---
```{r}

# Time Series
rain_ts = ts(san.mon$p, frequency = 12, start = c(1971,1))
plot.ts(rain_ts)

# Decomposing time series into trend,seasonality and randomness assuming additive model
rain_ts_components= decompose(rain_ts, type = "multiplicative")
plot(rain_ts_components)

# ACF and PACF of data
# par(mfrow=c(1,3))
acf(rain_ts, lag.max=20)
pacf(rain_ts, lag.max=20)
```

# Building ARIMA model 
```{r}

# Calculating ndiffs and nsdiffs using forecast
ndiffs(rain_ts)
nsdiffs(rain_ts)

# # ACF and PACF plots show trend and seasonility
# # Performing differences to make the data stationary
# # calculating "d "for Trend
# par(mfrow = c(1, 1))
# rain_ts_diff1 = diff(rain_ts, differences = 1)
# plot(rain_ts_diff1)
# 
# # Checking ACF and PACF for after differencing for above values 
# par(mfrow=c(1,2))
# acf(rain_ts_diff1, lag.max=20)
# pacf(rain_ts_diff1, lag.max=20)
# 
# # Performing seasonal differencing and checking for value of D
# par(mfrow = c(1, 1))
# rain_ts_seas_diff1 = diff(rain_ts, lag = 12, differences=1)
# plot(rain_ts_seas_diff1)
# 
# # Checking ACF and PACF for seasonally differenced data
# par(mfrow = c(1, 2))
# acf(rain_ts_seas_diff1)
# pacf(rain_ts_seas_diff1)



```


# No Differencing seasonally differenced data again
```{r}

# Implementing ARIMA model
# auto.arima(rain_ts)
model.rain = Arima(rain_ts, order = c(0,0,1),seasonal = c(2,0,2), include.drift = FALSE)

# Checking residuals to ensure they are white noise
par(mfrow = c(1, 2))
acf(model.rain$residuals, lag.max = 24)
pacf(model.rain$residuals, lag.max = 24)
Box.test(model.rain$residuals, lag=24, type="Ljung-Box")

# Forecasting using Arima model
par(mfrow = c(1, 1))
rain_ts_forecast = forecast(model.rain, h= 144)
plot(rain_ts_forecast)

rain_ts_forecast$mean
library(pander)
pander(rain_ts_forecast$mean)

# write.csv(rain_forecast, "D:/HYDRO COMPLEXITY/R software/Github_Learning/MSc_Coastal_Drainage_Analysis-master/MSc_Coastal_Drainage_Analysis/mon_timeseries\\seasonal_rain_forecast.csv")

```

# Actual ET ---
```{r}

# Time Series
aet_ts = ts(san.mon$aet, frequency = 12, start = c(1971,1))
plot.ts(aet_ts)

# Decomposing time series into trend,seasonality and randomness assuming additive model
aet_ts_components= decompose(aet_ts, type = "additive")
plot(aet_ts_components)

# ACF and PACF of data
# par(mfrow=c(1,3))
plot.ts(aet_ts)
acf(aet_ts, lag.max=20)
pacf(aet_ts, lag.max=20)
```


# Building ARIMA model
```{r}

# Calculating ndiffs and nsdiffs
ndiffs(aet_ts)
nsdiffs(aet_ts)

# # ACF and PACF plots show trend and seasonility
# # Performing differences to make the data stationary
# # calculating "d "for Trend
# par(mfrow = c(1, 1))
# aet_ts_diff1 = diff(aet_ts, differences = 1)
# plot(aet_ts_diff1)
# 
# # Checking ACF and PACF for after differencing for above values 
# par(mfrow=c(1,2))
# acf(aet_ts_diff1, lag.max=20)
# pacf(aet_ts_diff1, lag.max=20)

# Performing seasonal differencing and checking for value of D
par(mfrow = c(1, 1))
aet_ts_seas_diff1 = diff(aet_ts, lag = 12, differences = 1)
plot(aet_ts_seas_diff1)

# Checking ACF and PACF for seasonally differenced data
par(mfrow = c(1, 2))
acf(aet_ts_seas_diff1)
pacf(aet_ts_seas_diff1)


```

# Differencing seasonally differenced data again
```{r}

par(mfrow = c(1, 1))
aet_seas_diff = diff(aet_ts_seas_diff1, differences=1)
plot(aet_seas_diff)
par(mfrow = c(1, 2))
acf(aet_seas_diff)
pacf(aet_seas_diff)

# Implementing ARIMA model
# auto.arima(aet_ts)
model.aet = Arima(aet_ts, order = c(0,0,2),seasonal = c(1,1,1), include.drift = FALSE)

# Checking residuals to ensure they are white noise
par(mfrow = c(1, 2))
acf(model.aet$residuals, lag.max = 24)
pacf(model.aet$residuals, lag.max = 24)
Box.test(model.aet$residuals, lag=24, type="Ljung-Box")

# Forecasting using Arima model
par(mfrow = c(1, 1))
aet_ts_forecast = forecast(model.aet, h= 144)
plot(aet_ts_forecast)

aet_ts_forecast$mean
library(pander)
pander(aet_ts_forecast$mean)
```

# Potential ET ---
```{r}
# Time Series
pet_ts = ts(san.mon$pet, frequency = 12, start = c(1971,1))
plot.ts(pet_ts)

# Decomposing time series into trend,seasonality and randomness assuming additive model
pet_ts_components= decompose(pet_ts, type = "additive")
plot(pet_ts_components)

# ACF and PACF of data
# par(mfrow=c(1,3))
acf(pet_ts, lag.max=20)
pacf(pet_ts, lag.max=20)
```


# Building ARIMA model 
```{r}

# Calculating ndiffs and nsdiffs
ndiffs(pet_ts)
nsdiffs(pet_ts)

# # ACF and PACF plots show trend and seasonility
# # Performing differences to make the data stationary
# # calculating "d "for Trend
# par(mfrow = c(1, 1))
# pet_ts_diff1 = diff(pet_ts, differences = 1)
# plot(pet_ts_diff1)
# 
# # Checking ACF and PACF for after differencing for above values 
# par(mfrow=c(1,2))
# acf(pet_ts_diff1, lag.max=20)
# pacf(pet_ts_diff1, lag.max=20)

# Performing seasonal differencing and checking for value of D
par(mfrow = c(1, 1))
pet_ts_seas_diff1 = diff(pet_ts, lag = 12, differences=1)
plot(pet_ts_seas_diff1)

# Checking ACF and PACF for seasonally differenced data
par(mfrow = c(1, 2))
acf(pet_ts_seas_diff1)
pacf(pet_ts_seas_diff1)
```

# Differencing seasonaaly differenced data again
```{r}
par(mfrow = c(1, 1))
pet_seas_diff <- diff(pet_ts_seas_diff1, differences = 1)
plot(pet_seas_diff)
par(mfrow = c(1, 2))
acf(pet_seas_diff)
pacf(pet_seas_diff)

# Implementing ARIMA model
# auto.arima(pet_ts)
pet.model <- Arima(pet_ts, order = c(1,0,0),seasonal = c(2,1,2), include.drift = FALSE)

# Checking residuals to ensure they are white noise
par(mfrow = c(1, 2))
acf(pet.model$residuals, lag.max = 24)
pacf(pet.model$residuals, lag.max = 24)
Box.test(pet.model$residuals, lag=24, type="Ljung-Box")

# Forecasting using Arima model
par(mfrow = c(1, 1))
pet_ts_forecast = forecast(pet.model, h= 144)
plot(pet_ts_forecast)

pet_ts_forecast$mean
library(pander)
pander(pet_ts_forecast$mean)
```


# San Vitale ---
```{r}
# Time Series
san_ts = ts(san.mon$pu, frequency = 12, start = c(1971,1))

# imputeTS: Time Series Missing Value; Imputation in R by Steffen Moritz and Thomas Bartz-Beielstein
san_ts.imp <- na_kalman(san_ts)
san_imp <- ggplot_na_imputations(san_ts, san_ts.imp) + theme_cowplot()
plot.ts(san_ts.imp)
san_imp

# Decomposing time series into trend,seasonality and randomness assuming multiplicative model
san_ts_components= decompose(san_ts.imp, type = "additive")
plot(san_ts_components)

# ACF and PACF of data
# par(mfrow=c(1,3))
acf(san_ts.imp, lag.max=20)
pacf(san_ts.imp, lag.max=20)
```

# Building ARIMA model 
```{r}

# Calculating ndiffs and nsdiffs
ndiffs(san_ts.imp)
nsdiffs(san_ts.imp)

# ACF and PACF plots show trend and seasonility
# Performing differences to make the data stationary
# calculating "d "for Trend
par(mfrow = c(1, 1))
san_ts_diff1 = diff(san_ts.imp, differences = 1)
plot(san_ts_diff1)

# Checking ACF and PACF for after differencing for above values 
par(mfrow=c(1,2))
acf(san_ts_diff1, lag.max=20)
pacf(san_ts_diff1, lag.max=20)

# # Performing seasonal differencing and checking for value of D
# par(mfrow = c(1, 1))
# san_ts_seas_diff1 = diff(san_ts.imp, lag = 12, differences = 1)
# plot(san_ts_seas_diff1)
# 
# # Checking ACF and PACF for seasonally differenced data
# par(mfrow = c(1, 2))
# acf(san_ts_seas_diff1)
# pacf(san_ts_seas_diff1)


```

# No Differencing seasonally differenced data again
```{r}

# par(mfrow = c(1, 1))
# san_seas_diff = diff(san_ts_seas_diff1, differences=1)
# plot(san_seas_diff)
# par(mfrow = c(1, 2))
# acf(san_seas_diff)
# pacf(san_seas_diff)

# Implementing ARIMA model
# auto.arima(san_ts.imp)
san.model= Arima(san_ts.imp, order = c(1,1,1),seasonal = c(1,0,1), include.drift = FALSE)

# Checking residuals to ensure they are white noise
par(mfrow = c(1, 2))
acf(san.model$residuals, lag.max = 24)
pacf(san.model$residuals, lag.max = 24)
Box.test(san.model$residuals, lag=24, type="Ljung-Box")

# Forecasting using Arima model
par(mfrow = c(1, 1))
san_ts_forecast=forecast(san.model,h= 144)
plot(san_ts_forecast)

san_ts_forecast$mean
library(pander)
pander(san_ts_forecast$mean)

```


# Rasponi ----
```{r}
# Time Series
ras_ts = ts(ras.mon$pu, frequency = 12, start = c(1971,1))

# imputeTS: Time Series Missing Value; Imputation in R by Steffen Moritz and Thomas Bartz-Beielstein
ras_ts.imp <- na_kalman(ras_ts)
ggplot_na_imputations(ras_ts, ras_ts.imp) + theme_cowplot()
plot.ts(ras_ts.imp)

# Decomposing time series into trend,seasonality and randomness assuming additive model
ras_ts_components= decompose(ras_ts.imp, type = "additive")
plot(ras_ts_components)

# ACF and PACF of data
# par(mfrow=c(1,3))
acf(ras_ts.imp, lag.max=20)
pacf(ras_ts.imp, lag.max=20)
```

# Building ARIMA model 
```{r}

# Calculating ndiffs and nsdiffs
ndiffs(ras_ts.imp)
nsdiffs(ras_ts.imp)

# # ACF and PACF plots show trend and seasonility
# # Performing differences to make the data stationary
# # calculating "d "for Trend
# par(mfrow = c(1, 1))
# ras_ts_diff1 = diff(ras_ts.imp, differences = 1)
# plot(ras_ts_diff1)
# 
# # Checking ACF and PACF for after differencing for above values 
# par(mfrow=c(1,2))
# acf(ras_ts_diff1, lag.max=20)
# pacf(ras_ts_diff1, lag.max=20)
# 
# # Performing seasonal differencing and checking for value of D
# par(mfrow = c(1, 1))
# ras_ts_seas_diff1=diff(ras_ts.imp, lag = 12, differences=1)
# plot(ras_ts_seas_diff1)
# 
# # Checking ACF and PACF for seasonally differenced data
# par(mfrow = c(1, 2))
# acf(ras_ts_seas_diff1)
# pacf(ras_ts_seas_diff1)

```

# No Differencing seasonaaly differenced data again
```{r}

# Implementing ARIMA model
# auto.arima(ras_ts.imp)
ras.model= Arima(ras_ts.imp, order = c(4,0,0),seasonal = c(1,0,1), include.drift = FALSE)

# Checking residuals to ensure they are white noise
par(mfrow = c(1, 2))
acf(ras.model$residuals, lag.max = 24)
pacf(ras.model$residuals, lag.max = 24)
Box.test(ras.model$residuals, lag=24, type="Ljung-Box")

# Forecasting using Arima model
par(mfrow = c(1, 1))
ras_ts_forecast=forecast(ras.model,h= 144)
plot(ras_ts_forecast)

ras_ts_forecast$mean
library(pander)
pander(ras_ts_forecast$mean)
```


# Quinto ---
```{r}
# Time Series
quin_ts = ts(quin.mon$pu, frequency = 12, start = c(1971,1))
plot.ts(quin_ts)

# Decomposing time series into trend,seasonality and randomness assuming additive model
quin_ts_components= decompose(quin_ts, type = "additive")
plot(quin_ts_components)

# ACF and PACF of data
# par(mfrow=c(1,3))
acf(quin_ts, lag.max=20)
pacf(quin_ts, lag.max=20)
```

# Building ARIMA model
```{r}

# Calculating ndiffs and nsdiffs
ndiffs(quin_ts)
nsdiffs(quin_ts)

# ACF and PACF plots show trend and seasonility
# Performing differences to make the data stationary
# calculating "d "for Trend
par(mfrow = c(1, 1))
quin_ts_diff1 = diff(quin_ts, differences = 1)
plot(quin_ts_diff1)

# Checking ACF and PACF for after differencing for above values 
par(mfrow=c(1,2))
acf(quin_ts_diff1, lag.max=20)
pacf(quin_ts_diff1, lag.max=20)

# # Performing seasonal differencing and checking for value of D
# par(mfrow = c(1, 1))
# quin_ts_seas_diff1 = diff(quin_ts, lag = 12, differences=1)
# plot(quin_ts_seas_diff1)
# 
# # Checking ACF and PACF for seasonally differenced data
# par(mfrow = c(1, 2))
# acf(quin_ts_seas_diff1)
# pacf(quin_ts_seas_diff1)


```

# No Differencing seasonally differenced data again

```{r}
# par(mfrow = c(1, 1))
# quin_seas_diff = diff(quin_ts_seas_diff1, differences=1)
# plot(quin_seas_diff)
# par(mfrow = c(1, 2))
# acf(quin_seas_diff)
# pacf(quin_seas_diff)

# Implementing ARIMA model
# auto.arima(quin_ts)
quin.model <- Arima(quin_ts, order = c(1,1,1),seasonal = c(1,0,1), include.drift = FALSE)

# Checking residuals to ensure they are white noise
par(mfrow = c(1, 2))
acf(quin.model$residuals, lag.max = 24)
pacf(quin.model$residuals, lag.max = 24)
Box.test(quin.model$residuals, lag=24, type="Ljung-Box")

# Forecasting using Arima model
par(mfrow = c(1, 1))
quin_ts_forecast <- forecast(quin.model, h= 144)
plot(quin_ts_forecast)

quin_ts_forecast$mean
library(pander)
pander(quin_ts_forecast$mean)
```
